### 2017-08-11 README.Rmd
Merge branch 'master' into devel
* master: (100 commits)
  use precise with vignette and tests
  use precise
  no tests nor vignettes to try to build on travis
  update pkgdown
  readMSData2 is now deprecated
  fix typo in example
  update pkddown docs
  fix introduced bug
  remove trailing spaces
  Fix signature for pData<-,Chromatogram (issue #244)
  update scripts to set mode when reading data
  add alias from pData<-,MSnSet,data.frame
  readMSData gets a mode - see issue #233
  check MSnSet validity when replacing pData - closes issue #242
  update README and home page
  only show github (

[**MSnbase**](http://lgatto.github.io/MSnbase/) is an R/Bioconductor
package that provides infrastructure for plotting, data manipulation
and processing mass spectrometry and proteomics data. The project was
started by [Laurent Gatto](http://lgatto.github.io/) in October 2010
(Mon Oct 4 23:35:23 2010, according to the git log) and has, since
then, benefited from [various
contributions](http://lgatto.github.io/msnbase-contribs/).

The official page is the Bioconductor landing page
([release](http://www.bioconductor.org/packages/release/bioc/html/MSnbase.html)
or
[devel](http://www.bioconductor.org/packages/devel/bioc/html/MSnbase.html)
versions). The [github page](https://github.com/lgatto/MSnbase) page
is for sharing, testing, issue tracking and forking/pulling
purposes. The
[Bioconductor svn server](https://hedgehog.fhcrc.org/bioconductor/trunk/madman/Rpacks/),
is the official repository for the working source code.

@@

Contributions to the package are more than welcome. If you want to
contribute to this package, you should follow the same conventions as
the rest of the functions whenever it makes sense to do so. Feel free
to get in touch (preferable opening a
[github issue](https://github.com/lgatto/MSnbase/issues/)) to discuss
any suggestions. The
[`MSnbase` development vignette](http://lgatto.github.io/MSnbase/articles/MSnbase-development.html)
gives some background on the class infrastructure.

>>>>

[**MSnbase**](http://lgatto.github.io/MSnbase/) is an R/Bioconductor
package that provides infrastructure for plotting, manipulation and
processing mass spectrometry and proteomics data. The project was
started by [Laurent Gatto](http://lgatto.github.io/) in October 2010
(Mon Oct 4 23:35:23 2010, according to the git log) and has, since
then, benefited
from
[various contributions](http://lgatto.github.io/msnbase-contribs/), in
particular [Sebastian Gibb](http://sebastiangibb.de/)
and [Johannes Rainer](https://github.com/jotsetung/).

The official page is the Bioconductor landing page
([release](http://www.bioconductor.org/packages/release/bioc/html/MSnbase.html) or
[devel](http://www.bioconductor.org/packages/devel/bioc/html/MSnbase.html) versions). The
[github page](https://github.com/lgatto/MSnbase) page is for active
development, issue tracking and forking/pulling
purposes.

@@

Contributions to the package are more than welcome. If you want to
contribute to this package, you should follow the same conventions as
the rest of the functions. Please do get in touch (preferable opening
a [github issue](https://github.com/lgatto/MSnbase/issues/)) to
discuss any
suggestions. The
[`MSnbase` development vignette](http://lgatto.github.io/MSnbase/articles/MSnbase-development.html) gives
some background on the class infrastructure.
